% @Author: AnthonyKenny98
% @Date:   2020-02-22 15:42:12
% @Last Modified by:   AnthonyKenny98
% @Last Modified time: 2020-03-01 14:01:59

This thesis aims to design hardware that executes motion planning algorithms faster than those same algorithms can execute on generic hardware. Chatper 2 introduces motion planning and details the process of implementing and analysing \ac{RRT} to identify computational hot-spots in the algorithm and thus identify the biggest opportunities for hardware optimization. \\
Section \ref{section:motion_planning_background} provides an introduction to Motion Planning Algorithms in general. Section \ref{section:rrt} outlines the \ac{RRT} algorithm, and describes the implementation of \ac{RRT} for this project. Finally, Section \ref{section:rrt_analysis} outlines a method for performance analysis of \ac{RRT} and the results of such analysis.
\todo[inline]{Write a better introduction that more accurately defines sections and makes the POINT of this chapter clear.}

\section{Background} 
\label{section:motion_planning_background}
    Motion Planning Algorithms refer to the set of algorithms that find possible sequences of valid configurations for a robot in a space.
    \newline
    \newline
    \todo[inline,caption={Background on Motion Planning Algorithms.}]{Need more background here. Needs more of a mathematical foundation}

\newpage
\section{Rapidly-Exploring Random Tree}
\label{section:rrt}
    \input{chapters/chapter2/rrt}

\newpage
\section{Performance Analysis}
\label{section:rrt_analysis}
    \input{chapters/chapter2/rrt_analysis}